DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
reviewed benchmarks description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Our experimental evaluation consist of a set of control system benchmarks and  is  composed by 18 MIMO models extracted from the literature~\cite{bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
which include physical plants for UAV (unammed aerial vehicle), cruise control system, spring-mass damper, satellite, direct current (DC) servo motor, helicopter, inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, voltage regulator, and an acrobot control system~\cite{abate2017, abatecav2017}.

>>>>

Our experimental evaluation consists of $18$ SISO control system benchmarks 
extracted from the literature~\cite{abate2017, abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
voltage regulator, and an acrobot control system.
